Maximum Allowable Current Determination of Arbitrary Reconfigurable Battery Systems By Using a Directed Graph Model Combined with Greedy Algorithm

### 2023-06-30 paper/main.tex
向 SST 投稿

\documentclass{article}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{enumerate}
\usepackage{amsmath}
\DeclareMathOperator{\diag}{diag}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{footnote}
\usepackage{bm}
\usepackage[ruled,linesnumbered]{algorithm2e}
\setcounter{MaxMatrixCols}{20}
\usepackage{tikz}
\usetikzlibrary{arrows.meta, calc, fit, positioning, quotes, graphs, shapes.geometric}
\def\T{\mathrm{T}}

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{../attachments/stru-V-origin.png} % 完整结构
        \caption{}
        \label{fig:stru-Visairo}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{../attachments/stru-V-serial.png} % 全串联
        \caption{}
        \label{fig:stru-Visairo-serial}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{../attachments/stru-V-parallel.png} % 全并联
        \caption{}
        \label{fig:stru-Visairo-parallel}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{../attachments/stru-V-isolate} % 电池隔离 右二 B3 全并联
        \caption{}
        \label{fig:stru-Visairo-isolate}
    \end{subfigure}
    \caption{
        (a) The RBS structure proposed by Visairo\cite{visairoReconfigurableBatteryPack2008}, with
        all batteries in (b) series connection, (c) parallel connection, and
        (d) battery $B_3$ isolated.
        }
    \label{fig:arch}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.8\textwidth}
        \includegraphics[width=\textwidth]{../attachments/main.png}
        \caption{}
        \label{fig:main}
    \end{subfigure}
    \caption{ 
        Diagram of this method, which contains four main steps.
    }
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.31\textwidth}
        \includegraphics[width=\textwidth]{../attachments/direct-graph-he.png}
        \caption{}
        \label{fig:direct-graph-he}
    \end{subfigure}
    \hspace{0.02\textwidth}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{../attachments/direct-graph-xu.png}
        \caption{}
        \label{fig:direct-graph-xu}
    \end{subfigure}
    \hspace{0.02\textwidth}
    \begin{subfigure}[b]{0.24\textwidth}
        \includegraphics[width=\textwidth]{../attachments/direct-graph-my.png}
        \caption{}
        \label{fig:direct-graph-my}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.8\textwidth}
        \includegraphics[width=\textwidth]{../attachments/battery_simple.png}
        \caption{}
        \label{fig:battery_simple}
    \end{subfigure}
    \caption{ 
        Directed graph models used in (a) He's work \cite{heExploringAdaptiveReconfiguration2013}, (b) our previous work , and (c) this paper.
        (d) The equivalent circuit of a battery in this method.
    }
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.2\textwidth}
        \includegraphics[width=\textwidth]{../attachments/stru-L-origin.png}
        \caption{}
        \label{fig:study-stru-Lawson}
    \end{subfigure}
    \hspace{0.02\textwidth}
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{../attachments/stru-V-origin.png}
        \caption{}
        \label{fig:study-stru-Visairo}
    \end{subfigure}
    \hspace{0.02\textwidth}
    \begin{subfigure}[b]{0.31\textwidth}
        \includegraphics[width=\textwidth]{../attachments/stru-my-origin.png}
        \caption{}
        \label{fig:study-stru-my}
    \end{subfigure}
    \caption{The 4-battery RBS structures proposed by (a)Lawson\cite{lawsonSoftwareConfigurableBattery2012}, (b)Visairo\cite{visairoReconfigurableBatteryPack2008} and (c)this paper.}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.28\textwidth}
        \includegraphics[width=\textwidth]{../attachments/ef-topo.png}
        \caption{}
        \label{fig:study-dirgraph-my}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}[b]{0.28\textwidth}
        \includegraphics[width=\textwidth]{../attachments/ef-sp1.png}
        \caption{}
        \label{fig:sp1}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}[b]{0.28\textwidth}
        \includegraphics[width=\textwidth]{../attachments/ef-sp2.png}
        \caption{}
        \label{fig:sp2}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.28\textwidth}
        \includegraphics[width=\textwidth]{../attachments/ef-sp3.png}
        \caption{}
        \label{fig:sp3}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}[b]{0.28\textwidth}
        \includegraphics[width=\textwidth]{../attachments/ef-sp4.png}
        \caption{}
        \label{fig:sp4}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}[b]{0.28\textwidth}
        \includegraphics[width=\textwidth]{../attachments/ef-mac.png}
        \caption{}
        \label{fig:study-results-my}
    \end{subfigure}
    \caption{
        For the RBS structure in Fig.\ref{fig:study-stru-my}, 
        (a)its directed graph 
        and the $SP$s (highlighted in red) of battery (b)$B_1$, (c)$B_2$, (d)$B_3$, (e)$B_4$.
        (f)The circuit of the RBS with its output reaching the MAC.
        }
    \label{fig:all-results-my}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.31\textwidth}
        \includegraphics[width=\textwidth]{../attachments/my-isolated-1.png}
        \caption{}
        \label{fig:my-isolated-1}
    \end{subfigure}
    \hspace{0.02\textwidth}
    \begin{subfigure}[b]{0.31\textwidth}
        \includegraphics[width=\textwidth]{../attachments/my-isolated-2b.png}
        \caption{}
        \label{fig:my-isolated-2b}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.31\textwidth}
        \includegraphics[width=\textwidth]{../attachments/my-isolated-2w.png}
        \caption{}
        \label{fig:my-isolated-2w}
    \end{subfigure}
    \hspace{0.02\textwidth}
    \begin{subfigure}[b]{0.31\textwidth}
        \includegraphics[width=\textwidth]{../attachments/my-isolated-3.png}
        \caption{}
        \label{fig:my-isolated-3}
    \end{subfigure}
    \caption{
        The circuit states of MACs when isolating (a)one, (b)two(best case), (c)two(worst case) and (d)three batteries for the structure in Fig.\ref{fig:study-stru-my}.
        }
\end{figure}

>>>>

\documentclass{article}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{enumerate}
\usepackage{amsmath}
\DeclareMathOperator{\diag}{diag}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{footnote}
\usepackage{bm}
\usepackage[ruled,linesnumbered]{algorithm2e}
\setcounter{MaxMatrixCols}{20}
\usepackage{tikz}
\usetikzlibrary{arrows.meta, calc, fit, positioning, quotes, graphs, shapes.geometric}
\def\T{\mathrm{T}}
\graphicspath{ {../attachments/} }

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{stru-V-origin} % 完整结构
        \caption{}
        \label{fig:stru-Visairo}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{stru-V-serial} % 全串联
        \caption{}
        \label{fig:stru-Visairo-serial}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{stru-V-parallel} % 全并联
        \caption{}
        \label{fig:stru-Visairo-parallel}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{stru-V-isolate} % 电池隔离 右二 B3 全并联
        \caption{}
        \label{fig:stru-Visairo-isolate}
    \end{subfigure}
    \caption{
        (a) The RBS structure proposed by Visairo\cite{visairoReconfigurableBatteryPack2008}, with
        all batteries in (b) series connection, (c) parallel connection, and
        (d) battery $B_3$ isolated.
        }
    \label{fig:arch}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.8\textwidth}
        \includegraphics[width=\textwidth]{main}
        \caption{}
        \label{fig:main}
    \end{subfigure}
    \caption{ 
        Diagram of this method, which contains four main steps.
    }
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.31\textwidth}
        \includegraphics[width=\textwidth]{direct-graph-he}
        \caption{}
        \label{fig:direct-graph-he}
    \end{subfigure}
    \hspace{0.02\textwidth}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{direct-graph-xu}
        \caption{}
        \label{fig:direct-graph-xu}
    \end{subfigure}
    \hspace{0.02\textwidth}
    \begin{subfigure}[b]{0.24\textwidth}
        \includegraphics[width=\textwidth]{direct-graph-my}
        \caption{}
        \label{fig:direct-graph-my}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.8\textwidth}
        \includegraphics[width=\textwidth]{battery_simple}
        \caption{}
        \label{fig:battery_simple}
    \end{subfigure}
    \caption{ 
        Directed graph models used in (a) He's work \cite{heExploringAdaptiveReconfiguration2013}, (b) our previous work , and (c) this paper.
        (d) The equivalent circuit of a battery in this method.
    }
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.2\textwidth}
        \includegraphics[width=\textwidth]{stru-L-origin}
        \caption{}
        \label{fig:study-stru-Lawson}
    \end{subfigure}
    \hspace{0.02\textwidth}
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{stru-V-origin}
        \caption{}
        \label{fig:study-stru-Visairo}
    \end{subfigure}
    \hspace{0.02\textwidth}
    \begin{subfigure}[b]{0.31\textwidth}
        \includegraphics[width=\textwidth]{stru-my-origin}
        \caption{}
        \label{fig:study-stru-my}
    \end{subfigure}
    \caption{The 4-battery RBS structures proposed by (a)Lawson\cite{lawsonSoftwareConfigurableBattery2012}, (b)Visairo\cite{visairoReconfigurableBatteryPack2008} and (c)this paper.}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.28\textwidth}
        \includegraphics[width=\textwidth]{ef-topo}
        \caption{}
        \label{fig:study-dirgraph-my}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}[b]{0.28\textwidth}
        \includegraphics[width=\textwidth]{ef-sp1}
        \caption{}
        \label{fig:sp1}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}[b]{0.28\textwidth}
        \includegraphics[width=\textwidth]{ef-sp2}
        \caption{}
        \label{fig:sp2}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.28\textwidth}
        \includegraphics[width=\textwidth]{ef-sp3}
        \caption{}
        \label{fig:sp3}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}[b]{0.28\textwidth}
        \includegraphics[width=\textwidth]{ef-sp4}
        \caption{}
        \label{fig:sp4}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}[b]{0.28\textwidth}
        \includegraphics[width=\textwidth]{ef-mac}
        \caption{}
        \label{fig:study-results-my}
    \end{subfigure}
    \caption{
        For the RBS structure in Fig.\ref{fig:study-stru-my}, 
        (a)its directed graph 
        and the $SP$s (highlighted in red) of battery (b)$B_1$, (c)$B_2$, (d)$B_3$, (e)$B_4$.
        (f)The circuit of the RBS with its output reaching the MAC.
        }
    \label{fig:all-results-my}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.31\textwidth}
        \includegraphics[width=\textwidth]{my-isolated-1}
        \caption{}
        \label{fig:my-isolated-1}
    \end{subfigure}
    \hspace{0.02\textwidth}
    \begin{subfigure}[b]{0.31\textwidth}
        \includegraphics[width=\textwidth]{my-isolated-2b}
        \caption{}
        \label{fig:my-isolated-2b}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.31\textwidth}
        \includegraphics[width=\textwidth]{my-isolated-2w}
        \caption{}
        \label{fig:my-isolated-2w}
    \end{subfigure}
    \hspace{0.02\textwidth}
    \begin{subfigure}[b]{0.31\textwidth}
        \includegraphics[width=\textwidth]{my-isolated-3}
        \caption{}
        \label{fig:my-isolated-3}
    \end{subfigure}
    \caption{
        The circuit states of MACs when isolating (a)one, (b)two(best case), (c)two(worst case) and (d)three batteries for the structure in Fig.\ref{fig:study-stru-my}.
        }
\end{figure}
